Estimating Comparative Advantage in Improved Seed Adoption: Hybrid Maize in Ethiopia

### 2021-11-24 paper.tex
Updates from Overleaf

Figure \ref{map:regions} shows the spatial distribution of the locations of the our households of study. The number of households surveyed did

\begin{figure}
    \centering
    \includegraphics{results/figures/map_hhids.pdf}
    \caption{Mean Spatial Distribution of Households across Ethiopia}
    \label{map:regions}
\end{figure}

>>>>

Figure \ref{map:regions} shows the spatial distribution of the locations of the our households of study. As previously mentioned these are households that grow either improved or conventional maize and that are observed for all three rounds of the survey. Most households come from the northwest region of the

\begin{figure}
    \centering
    \includegraphics{results/figures/map_hhids.pdf}
    \caption{Spatial Distribution of Households Surveyed}
    \label{map:regions}
\end{figure}
